---
title: "Assignment_B4"
author: "Jacky Yiu"
date: "2023-12-02"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prerequisites

Please install the following libraries

```{r}
library(dplyr)
library(janeaustenr)
library(ggplot2)
library(tidytext)
library(testthat)
library(viridis)
library(stringr)
```

# Option A -- Strings and functional programming in R

## **Exercise 1 (37.5 points) - Jane Austen Word Count**

For this exercise I pick the novel "Sense and Sensibility" from the `janeaustenr` library.

I will first make `janeaustenr::sensesensibility` into a tibble to see what the data looks like.

```{r}
sensesensibility_tibble <- tibble(txt = sensesensibility)
sensesensibility_tibble
```

It seem like every row contain sentence instead of inidvidual words, To convert the sentence into individual words and ignore all punctuation and white space, I will use the function `unnest_tokens` from the `tidytext` package.

It also make all word lower case so it does discriminate uppercase and lower case words.

```{r}
sensesensibility_words <- tidytext::unnest_tokens(sensesensibility_tibble, word, txt)
head(sensesensibility_words)
```

As per the exercise requirement, I will use remove "stop words" from the book using the list from `tidytext::stop_words`

I will use anti-join to exclude all words in `sensesensibility_word` that is also in `tidytext::stop_words`

```{r}
sensesensibility_no_stopwords <- anti_join(sensesensibility_words , tidytext::stop_words, by="word")
head(sensesensibility_no_stopwords)
```

Next, I will find out the Top 20 words using the following code, than use `str_to_title` from the `stringr` package to capitalize wach word to make it more pretty

```{r}
sensesensibility_no_stopwords_top_words <- sensesensibility_no_stopwords %>%
  count(word, sort = TRUE) %>%
  top_n(20)

sensesensibility_no_stopwords_top_words$word <- str_to_title(sensesensibility_no_stopwords_top_words$word)
sensesensibility_no_stopwords_top_words
```

Finally, using GGplot, histogram, we can visualize the data.

```{r}
ggplot(sensesensibility_no_stopwords_top_words, aes(x = reorder(word, n), y = n, fill = n)) +
  geom_col(color = "black", show.legend = FALSE) +
  labs(title = "Top 20 Most Common Words in \"Sense and Sensibility\" (excluding stopwords)",
       x = "Word",
       y = "Frequency") +
  scale_fill_viridis_c()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))

```

## **Exercise 2 (37.5 points) Pig Latin**

I define my customized Pig Latin function with the following rules:

1.  If the word begins with a vowel and end with vowel, append"oodle" to every vowel.

2.  If the word begins with a vowel and end with consonant, append"oodle" to every vowel , and add "acky" to the end. .

3.  If the word begins with a consonant, move the first consonant to the end and the last letter to the beginning, append"oodle" to every vowel and add "-acky" to the end.

```{r}
#' Custom Pig Latin Transformation
#'
#' This function transforms a word into Pig Latin based on my customized Pig Latin function with the following rules:
#' 
#' 1. If the word begins with a vowel and ends with a vowel, append "oodle-" to every vowel.
#' 2. If the word begins with a vowel and ends with a consonant, append "oodle-" to every vowel and add "acky" to the end.
#' 3. If the word begins with a consonant, move the first consonant to the end and the last letter to the beginning, append "oodle-" to every vowel, and add "acky" to the end.
#' 
#' The function also ensures that if the original word is capitalized, the transformed word will also be capitalized.
#' 
#' @param word A character string representing the input word (must be a single word).
#' 
#' @return A character string representing the word transformed into Pig Latin.
#' 
#' @examples
#' customPigLatin("Example")
#' # Returns: "Eoodle-Xoodle-Mpleoodle"
#' 
#' @export

customPigLatin <- function(word) {
  # Ensure that the input is a character string
  if (!is.character(word) || length(word) != 1) {
    stop("Input must be a character string.")
  }
  
  # Ensure that the input is a single word
  if (length(str_split(word, "\\s")[[1]]) > 1) {
    stop("Input must be a single word.")
  }
  
  # Define a vector of vowels
  vowels <- c("a", "e", "i", "o", "u")

  # Check if the first letter is capitalized
  is_capitalized <- str_detect(word, "^[A-Z]")
  
  original <- tolower(word)

  # Extract the first letter of the word
  first_letter <- substr(original, 1, 1)

  if (first_letter %in% vowels) {
    # Rule 1: Word begins with a vowel and ends with a vowel
    if (substr(original, nchar(original), nchar(original)) %in% vowels) {
      # Append "oodle-" to every vowel
      result <- str_replace_all(original, "[aeiou]", "\\0oodle-")
    } else {
      # Rule 2: Word begins with a vowel and ends with a consonant
      # Append "oodle-" to every vowel and add "acky" to the end
      result <- str_replace_all(original, "[aeiou]", "\\0oodle-") %>%
        str_c("acky")
    }
  } else {
    # Rule 3: Word begins with a consonant
    # Move the first consonant to the end and the last letter to the beginning
    # Append "oodle-" to every vowel and add "acky" to the end
    first_consonant <- str_extract(original, "[^aeiou]")
    last_letter <- substr(original, nchar(original), nchar(original))
    middle_letters <- str_sub(original, 2, nchar(original) - 1)
    
    result <- str_c(last_letter, middle_letters, first_consonant) %>%
              str_replace_all("[aeiou]", "\\0oodle-") %>%
              str_c("acky")
  }

  # Use str_replace to remove a hyphen at the end of the word
  result <- str_replace(result, "-$", "")

  # Capitalize the first letter if the original word is capitalized
  if (is_capitalized) {
    result <- paste0(toupper(substr(result, 1, 1)), substr(result, 2, nchar(result)))
  }

  return(result)
}

```

Here are some example

```{r}
#Example
word1 <- "apple" #Start and end with vowel (RULE 1)
word2 <- "table" #Start with consonant and end with vowel (RULE 3)
word3 <- "Elephant" #Start with vowel, end with with consonant (RULE 2)
word4 <- "Dog" #Start and end with consonant (RULE 3)

pig_latin_result1 <- customPigLatin(word1)
pig_latin_result2 <- customPigLatin(word2)
pig_latin_result3 <- customPigLatin(word3)
pig_latin_result4 <- customPigLatin(word4)

cat(sprintf("Original: %s, Pig Latin: %s\n", word1, pig_latin_result1))
cat(sprintf("Original: %s, Pig Latin: %s\n", word2, pig_latin_result2))
cat(sprintf("Original: %s, Pig Latin: %s\n", word3, pig_latin_result3))
cat(sprintf("Original: %s, Pig Latin: %s\n", word4, pig_latin_result4))
```

Next we create various non-redundant test cases

```{r}
test_that("Custom Pig Latin Transformation", {
  
  # Test with a phrase instead of a single word
  non_single_word <- "Hello world"
  expect_error(customPigLatin(non_single_word), "Input must be a single word.")
  
  # Test with a number instead of charater
  non_character <- 5486546
  expect_error(customPigLatin(non_character), "Input must be a character string.")
  
  # Rule 1: Word begins with a vowel and ends with a vowel
  input_word_1 <- "able"
  expected_result_1 <- "aoodle-bleoodle"
  actual_result_1 <- customPigLatin(input_word_1)
  expect_equal(actual_result_1, expected_result_1)

  # Rule 2: Word begins with a vowel and ends with a consonant
  input_word_2 <- "Ironman"
  expected_result_2 <- "Ioodle-rooodle-nmaoodle-nacky"
  actual_result_2 <- customPigLatin(input_word_2)
  expect_equal(actual_result_2, expected_result_2)

  # Rule 3: Word begins with a consonant
  input_word_3 <- "Tiger"
  expected_result_3 <- "Rioodle-geoodle-tacky"
  actual_result_3 <- customPigLatin(input_word_3)
  expect_equal(actual_result_3, expected_result_3)
})
```
